---
title: "Stem Maps Cleaning"
author: Alexandria Pawlik (apawlik@umich.edu)
---

Basic data cleaning for stemmaps excel export 
```{r}
library(stringr)
library(dplyr)
library(readr)
options("digits" = 15)
dt <- read_csv("../raw/stemmaps_export.csv", col_types = 'cccccidddddd')
```

Clean column headers
```{r}
names(dt)
names(dt) <- str_to_title(names(dt))
names(dt)[12] <- "Elevation"
names(dt)[5] <- "TreeID"
# names(dt)
```

Categorical variable consistency and numerical rounding
```{r}
# consistent case
dt <- mutate(dt, Species = toupper(Species)) 

# replace some values
dt$Location[dt$Location == "AnnArbor"] <- "AA"
dt$Species[dt$Species == "AMSPP."] <- "AMSP."
dt$Species[dt$Species == "BESP"] <- "BESP."
dt$Species[dt$Species == "SALIX SPP"] <- "SASP."

# rounding
dt$Diameter = round(dt$Diameter, digits=1)
dt$Xplot = round(dt$Xplot, digits=1)
dt$Yplot = round(dt$Yplot, digits=1)
dt$Latitude = round(dt$Latitude, digits=3)
dt$Longitude = round(dt$Longitude, digits=3)
dt$Elevation = round(dt$Elevation, digits=6)

head(dt)
```

Export
```{r}
write.csv(dt, file = "../output/stemmaps.csv", eol = "\r", row.names = FALSE)
```

Following the cleaning done in this notebook, lat and long columns were removed from the table and replaced with x_point_MichGeoRef and y_point_MichGeoRef. This dataset has been reprojected to Michigan GeoRef (meters) which is more appropriate for mapping features in Michigan. Here's some info: https://www.michigan.gov/documents/DNR_Map_Proj_and_MI_Georef_Info_20889_7.pdf

Version 2 cleaning
```{r}
dt <- read_csv("../versions/stemMaps_v2.csv", col_types = "-cccdcidddddd")
head(dt)
names(dt)[11] <- "X_Georef_Coor"
names(dt)[12] <- "Y_Georef_Coor"
write.csv(dt, file = "../output/stemMaps.csv", eol = "\r", row.names = FALSE)
```



